A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-24 paper/draft.tex
set up new pipeline for data

\subsection{Prevalence of Patronage}
\label{sec:prevalence_patronage}

@@

Alongside these spatial differences, there are

\begin{figure}[H]
    \centering
    \includegraphics[width = 8cm, height = 8cm]{figures/partisanship/plot_partisanship_by_cbo_group.pdf}
    \caption{\textbf{Proportion of party-affiliated members by occupation}. Darker colors indicate a larger degree of partisan affiliation. Sample includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}

>>>>

\subsection{Islands of Patronage}
\label{sec:prevalence_patronage}

@@

Alongside these spatial differences, there are significant differences with respect to the types of positions occupied by party members. Figure \ref{fig:partisan_by_cbo} breaks down the distribution of party members across different levels of the bureaucracy, using CBO (occupation) classifications provided by the RAIS data. Bureaucrat high corresponds to high-level management positions, such as directors and managers, bureaucrat low are low-level management such as supervisors and clerks. Frontline providers includes all types of service providers, where frontline high includes doctors and teachers, while low are other service providers such as janitors or security guards.

Party members are relatively concentrated in high level bureaucrat positions, such as managers and directors. These are also the best

\begin{figure}[H]
    \centering
    \includegraphics[width = 8cm, height = 8cm]{figures/partisanship/plot_partisanship_by_cbo_group.pdf}
    \caption{\textbf{Proportion of party-affiliated members by occupation}. Darker colors indicate a larger degree of partisan affiliation. Sample includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:partisan_by_cbo}
\end{figure}
